% Shared bibliography — all venues use the same references

\bibliographystyle{plain}
% \bibliography{references}  % Uncomment when references.bib exists

% Temporary inline references for skeleton
\begin{thebibliography}{99}

\bibitem{wang2023bitnet}
H.~Wang et al.
\newblock BitNet: Scaling 1-bit Transformers for Large Language Models.
\newblock \emph{arXiv:2310.11453}, 2023.

\bibitem{ma2024bitnetb158}
S.~Ma et al.
\newblock The Era of 1-bit LLMs: All Large Language Models are in 1.58 Bits.
\newblock \emph{arXiv:2402.17764}, 2024.

\bibitem{courbariaux2015binaryconnect}
M.~Courbariaux et al.
\newblock BinaryConnect: Training Deep Neural Networks with Binary Weights during Propagations.
\newblock \emph{NeurIPS}, 2015.

\bibitem{rastegari2016xnornet}
M.~Rastegari et al.
\newblock XNOR-Net: ImageNet Classification Using Binary Convolutional Neural Networks.
\newblock \emph{ECCV}, 2016.

\bibitem{li2016ternary}
F.~Li et al.
\newblock Ternary Weight Networks.
\newblock \emph{arXiv:1605.04711}, 2016.

\bibitem{krizhevsky2009cifar}
A.~Krizhevsky.
\newblock Learning Multiple Layers of Features from Tiny Images.
\newblock Technical report, 2009.

\bibitem{devries2017cutout}
T.~DeVries and G.~Taylor.
\newblock Improved Regularization of Convolutional Neural Networks with Cutout.
\newblock \emph{arXiv:1708.04552}, 2017.

\bibitem{cubuk2019autoaugment}
E.~Cubuk et al.
\newblock AutoAugment: Learning Augmentation Strategies from Data.
\newblock \emph{CVPR}, 2019.

\bibitem{cubuk2020randaugment}
E.~Cubuk et al.
\newblock RandAugment: Practical Automated Data Augmentation with a Reduced Search Space.
\newblock \emph{NeurIPS}, 2020.

\bibitem{rw2019timm}
R.~Wightman.
\newblock PyTorch Image Models.
\newblock \url{https://github.com/rwightman/pytorch-image-models}, 2019.

\bibitem{he2016resnet}
K.~He et al.
\newblock Deep Residual Learning for Image Recognition.
\newblock \emph{CVPR}, 2016.

\bibitem{simonyan2014vgg}
K.~Simonyan and A.~Zisserman.
\newblock Very Deep Convolutional Networks for Large-Scale Image Recognition.
\newblock \emph{ICLR}, 2015.

\bibitem{sandler2018mobilenetv2}
M.~Sandler et al.
\newblock MobileNetV2: Inverted Residuals and Linear Bottlenecks.
\newblock \emph{CVPR}, 2018.

\bibitem{tan2019efficientnet}
M.~Tan and Q.~Le.
\newblock EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks.
\newblock \emph{ICML}, 2019.

\bibitem{hinton2015distilling}
G.~Hinton, O.~Vinyals, and J.~Dean.
\newblock Distilling the Knowledge in a Neural Network.
\newblock \emph{NeurIPS Deep Learning Workshop}, 2015.

\bibitem{zhu2017ttq}
C.~Zhu, S.~Han, H.~Mao, and W.~Dally.
\newblock Trained Ternary Quantization.
\newblock \emph{ICLR}, 2017.

\bibitem{kim2019qkd}
J.~Kim, Y.~Bhalgat, J.~Lee, C.~Patel, and N.~Kwak.
\newblock QKD: Quantization-aware Knowledge Distillation.
\newblock \emph{arXiv:1911.12491}, 2019.

\bibitem{wang2019haq}
K.~Wang, Z.~Liu, Y.~Lin, J.~Lin, and S.~Han.
\newblock HAQ: Hardware-Aware Automated Quantization with Mixed Precision.
\newblock \emph{CVPR}, 2019.

\bibitem{nielsen2024bitnetreloaded}
J.~Nielsen and P.~Schneider-Kamp.
\newblock BitNet b1.58 Reloaded: State-of-the-art Performance Also on Smaller Networks.
\newblock \emph{arXiv:2407.09527}, 2024.

\bibitem{kim2025bdnet}
D.~Kim, J.-S.~Lee, N.-r.~Kim, S.~Lee, and J.-H.~Lee.
\newblock BD-Net: Has Depth-Wise Convolution Ever Been Applied in Binary Neural Networks?
\newblock \emph{AAAI}, 2026.

\bibitem{zhou2016dorefa}
S.~Zhou, Y.~Wu, Z.~Ni, X.~Zhou, H.~Wen, and Y.~Zou.
\newblock DoReFa-Net: Training Low Bitwidth Convolutional Neural Networks with Low Bitwidth Gradients.
\newblock \emph{arXiv:1606.06160}, 2016.

\bibitem{dong2019hawq}
Z.~Dong, Z.~Yao, A.~Gholami, M.~Mahoney, and K.~Keutzer.
\newblock HAWQ: Hessian AWare Quantization of Neural Networks with Mixed-Precision.
\newblock \emph{ICCV}, 2019.

\bibitem{elthakeb2020dcq}
A.~T.~Elthakeb, P.~Pilligundla, F.~Mireshghallah, A.~Alaghi, and H.~Esmaeilzadeh.
\newblock Divide and Conquer: Leveraging Intermediate Feature Representations for Quantized Training of Neural Networks.
\newblock \emph{arXiv:1906.06033}, 2020.

\bibitem{blumenfeld2019meanfield}
Y.~Blumenfeld, D.~Gilboa, and D.~Soudry.
\newblock A Mean Field Theory of Quantized Deep Networks: The Quantization-Depth Trade-Off.
\newblock \emph{NeurIPS}, 2019.

\bibitem{tang2020understanding}
J.~Tang, S.~Shivanna, Z.~Zhao, D.~Lin, A.~Singh, E.~H.~Chi, and S.~Jain.
\newblock Understanding and Improving Knowledge Distillation.
\newblock \emph{arXiv:2002.03532}, 2020.

\bibitem{le2015tinyimagenet}
Y.~Le and X.~Yang.
\newblock Tiny ImageNet Visual Recognition Challenge.
\newblock CS 231N, Stanford University, 2015.

\bibitem{liu2020reactnet}
Z.~Liu, Z.~Shen, M.~Savvides, and K.-T.~Cheng.
\newblock ReActNet: Towards Precise Binary Neural Network with Generalized Activation Functions.
\newblock \emph{ECCV}, 2020.

\bibitem{martinez2020real2binary}
B.~Martinez, J.~Yang, A.~Bulat, and G.~Tzimiropoulos.
\newblock Training Binary Neural Networks with Real-to-Binary Convolutions.
\newblock \emph{ICLR}, 2020.

\bibitem{mirzadeh2020teacher}
S.~Mirzadeh, M.~Farajtabar, A.~Li, N.~Levine, A.~Matsukawa, and H.~Ghasemzadeh.
\newblock Improved Knowledge Distillation via Teacher Assistant.
\newblock \emph{AAAI}, 2020.

\bibitem{guo2022bnext}
N.~Guo, J.~Bethge, C.~Meinel, and H.~Yang.
\newblock BNext: Any Precision Binary Neural Network.
\newblock \emph{arXiv:2211.12933}, 2022.

\bibitem{liu2022convnext}
Z.~Liu, H.~Mao, C.-Y.~Wu, C.~Feichtenhofer, T.~Darrell, and S.~Xie.
\newblock A ConvNet for the 2020s.
\newblock \emph{CVPR}, 2022.

\bibitem{cho2019efficacy}
J.~H.~Cho and B.~Hariharan.
\newblock On the Efficacy of Knowledge Distillation.
\newblock \emph{ICCV}, 2019.

\bibitem{anderson2018binary}
A.~G.~Anderson and C.~P.~Berg.
\newblock The High-Dimensional Geometry of Binary Neural Networks.
\newblock \emph{ICLR}, 2018.

\bibitem{tishby2015deep}
N.~Tishby and N.~Zaslavsky.
\newblock Deep Learning and the Information Bottleneck Principle.
\newblock \emph{IEEE Information Theory Workshop}, 2015.

\bibitem{esser2020lsq}
S.~K.~Esser, J.~L.~McKinstry, D.~Bablani, R.~Appuswamy, and D.~S.~Modha.
\newblock Learned Step Size Quantization.
\newblock \emph{ICLR}, 2020.

\bibitem{choi2018pact}
J.~Choi, Z.~Wang, S.~Venkataramani, P.~I.-J.~Fong, V.~Srinivasan, and K.~Gopalakrishnan.
\newblock PACT: Parameterized Clipping Activation for Quantized Neural Networks.
\newblock \emph{arXiv:1805.06085}, 2018.

\bibitem{dong2020hawqv2}
Z.~Dong, Z.~Yao, D.~Arfeen, A.~Gholami, M.~W.~Mahoney, and K.~Keutzer.
\newblock HAWQ-V2: Hessian Aware trace-Weighted Quantization of Neural Networks.
\newblock \emph{NeurIPS}, 2020.

\bibitem{lee2021ewgs}
J.~Lee, D.~Kim, and B.~Ham.
\newblock Network Quantization with Element-wise Gradient Scaling.
\newblock \emph{CVPR}, 2021.

\bibitem{qin2020irnet}
H.~Qin, R.~Gong, X.~Liu, M.~Shen, Z.~Wei, F.~Yu, and J.~Song.
\newblock Forward and Backward Information Retention for Accurate Binary Neural Networks.
\newblock \emph{CVPR}, 2020.

\bibitem{zhao2024sqakd}
K.~Zhao and M.~Zhao.
\newblock SQAKD: Self-supervised Quantization-Aware Knowledge Distillation.
\newblock \emph{AISTATS}, 2024.

\end{thebibliography}
