% Minimal bibliography for NeurIPS Workshop (12 references only)

\bibliographystyle{plain}

\begin{thebibliography}{99}

\bibitem{ma2024bitnetb158}
S.~Ma et al.
\newblock The Era of 1-bit LLMs: All Large Language Models are in 1.58 Bits.
\newblock \emph{arXiv:2402.17764}, 2024.
\bibitem{courbariaux2015binaryconnect}
M.~Courbariaux et al.
\newblock BinaryConnect: Training Deep Neural Networks with Binary Weights during Propagations.
\newblock \emph{NeurIPS}, 2015.
\bibitem{rastegari2016xnornet}
M.~Rastegari et al.
\newblock XNOR-Net: ImageNet Classification Using Binary Convolutional Neural Networks.
\newblock \emph{ECCV}, 2016.
\bibitem{li2016ternary}
F.~Li et al.
\newblock Ternary Weight Networks.
\newblock \emph{arXiv:1605.04711}, 2016.
\bibitem{rw2019timm}
R.~Wightman.
\newblock PyTorch Image Models.
\newblock \url{https://github.com/rwightman/pytorch-image-models}, 2019.
\bibitem{hinton2015distilling}
G.~Hinton, O.~Vinyals, and J.~Dean.
\newblock Distilling the Knowledge in a Neural Network.
\newblock \emph{NeurIPS Deep Learning Workshop}, 2015.
\bibitem{zhu2017ttq}
C.~Zhu, S.~Han, H.~Mao, and W.~Dally.
\newblock Trained Ternary Quantization.
\newblock \emph{ICLR}, 2017.
\bibitem{kim2019qkd}
J.~Kim, Y.~Bhalgat, J.~Lee, C.~Patel, and N.~Kwak.
\newblock QKD: Quantization-aware Knowledge Distillation.
\newblock \emph{arXiv:1911.12491}, 2019.
\bibitem{wang2019haq}
K.~Wang, Z.~Liu, Y.~Lin, J.~Lin, and S.~Han.
\newblock HAQ: Hardware-Aware Automated Quantization with Mixed Precision.
\newblock \emph{CVPR}, 2019.
\bibitem{zhou2016dorefa}
S.~Zhou, Y.~Wu, Z.~Ni, X.~Zhou, H.~Wen, and Y.~Zou.
\newblock DoReFa-Net: Training Low Bitwidth Convolutional Neural Networks with Low Bitwidth Gradients.
\newblock \emph{arXiv:1606.06160}, 2016.
\bibitem{dong2019hawq}
Z.~Dong, Z.~Yao, A.~Gholami, M.~Mahoney, and K.~Keutzer.
\newblock HAWQ: Hessian AWare Quantization of Neural Networks with Mixed-Precision.
\newblock \emph{ICCV}, 2019.
\bibitem{dong2020hawqv2}
Z.~Dong, Z.~Yao, D.~Arfeen, A.~Gholami, M.~W.~Mahoney, and K.~Keutzer.
\newblock HAWQ-V2: Hessian Aware trace-Weighted Quantization of Neural Networks.
\newblock \emph{NeurIPS}, 2020.

\end{thebibliography}
