% Shared bibliography — all venues use the same references

\bibliographystyle{plain}
% \bibliography{references}  % Uncomment when references.bib exists

% Temporary inline references for skeleton
\begin{thebibliography}{99}

\bibitem{wang2023bitnet}
H.~Wang et al.
\newblock BitNet: Scaling 1-bit Transformers for Large Language Models.
\newblock \emph{arXiv:2310.11453}, 2023.

\bibitem{ma2024bitnetb158}
S.~Ma et al.
\newblock The Era of 1-bit LLMs: All Large Language Models are in 1.58 Bits.
\newblock \emph{arXiv:2402.17764}, 2024.

\bibitem{courbariaux2015binaryconnect}
M.~Courbariaux et al.
\newblock BinaryConnect: Training Deep Neural Networks with Binary Weights during Propagations.
\newblock \emph{NeurIPS}, 2015.

\bibitem{rastegari2016xnornet}
M.~Rastegari et al.
\newblock XNOR-Net: ImageNet Classification Using Binary Convolutional Neural Networks.
\newblock \emph{ECCV}, 2016.

\bibitem{li2016ternary}
F.~Li et al.
\newblock Ternary Weight Networks.
\newblock \emph{arXiv:1605.04711}, 2016.

\bibitem{krizhevsky2009cifar}
A.~Krizhevsky.
\newblock Learning Multiple Layers of Features from Tiny Images.
\newblock Technical report, 2009.

\bibitem{devries2017cutout}
T.~DeVries and G.~Taylor.
\newblock Improved Regularization of Convolutional Neural Networks with Cutout.
\newblock \emph{arXiv:1708.04552}, 2017.

\bibitem{cubuk2019autoaugment}
E.~Cubuk et al.
\newblock AutoAugment: Learning Augmentation Strategies from Data.
\newblock \emph{CVPR}, 2019.

\bibitem{cubuk2020randaugment}
E.~Cubuk et al.
\newblock RandAugment: Practical Automated Data Augmentation with a Reduced Search Space.
\newblock \emph{NeurIPS}, 2020.

\bibitem{he2016resnet}
K.~He et al.
\newblock Deep Residual Learning for Image Recognition.
\newblock \emph{CVPR}, 2016.

\bibitem{hinton2015distilling}
G.~Hinton, O.~Vinyals, and J.~Dean.
\newblock Distilling the Knowledge in a Neural Network.
\newblock \emph{NeurIPS Deep Learning Workshop}, 2015.

\bibitem{zhu2017ttq}
C.~Zhu, S.~Han, H.~Mao, and W.~Dally.
\newblock Trained Ternary Quantization.
\newblock \emph{ICLR}, 2017.

\bibitem{kim2019qkd}
J.~Kim, Y.~Bhalgat, J.~Lee, C.~Patel, and N.~Kwak.
\newblock QKD: Quantization-aware Knowledge Distillation.
\newblock \emph{arXiv:1911.12491}, 2019.

\bibitem{wang2019haq}
K.~Wang, Z.~Liu, Y.~Lin, J.~Lin, and S.~Han.
\newblock HAQ: Hardware-Aware Automated Quantization with Mixed Precision.
\newblock \emph{CVPR}, 2019.

\bibitem{nielsen2024bitnetreloaded}
J.~Nielsen and P.~Schneider-Kamp.
\newblock BitNet b1.58 Reloaded: State-of-the-art Performance Also on Smaller Networks.
\newblock \emph{arXiv:2407.09527}, 2024.

\bibitem{kim2025bdnet}
D.~Kim, J.-S.~Lee, N.-r.~Kim, S.~Lee, and J.-H.~Lee.
\newblock BD-Net: Has Depth-Wise Convolution Ever Been Applied in Binary Neural Networks?
\newblock \emph{AAAI}, 2026.

\bibitem{zhou2016dorefa}
S.~Zhou, Y.~Wu, Z.~Ni, X.~Zhou, H.~Wen, and Y.~Zou.
\newblock DoReFa-Net: Training Low Bitwidth Convolutional Neural Networks with Low Bitwidth Gradients.
\newblock \emph{arXiv:1606.06160}, 2016.

\bibitem{dong2019hawq}
Z.~Dong, Z.~Yao, A.~Gholami, M.~Mahoney, and K.~Keutzer.
\newblock HAWQ: Hessian AWare Quantization of Neural Networks with Mixed-Precision.
\newblock \emph{ICCV}, 2019.

\bibitem{elthakeb2020dcq}
A.~T.~Elthakeb, P.~Pilligundla, F.~Mireshghallah, A.~Alaghi, and H.~Esmaeilzadeh.
\newblock Divide and Conquer: Leveraging Intermediate Feature Representations for Quantized Training of Neural Networks.
\newblock \emph{arXiv:1906.06033}, 2020.

\bibitem{le2015tinyimagenet}
Y.~Le and X.~Yang.
\newblock Tiny ImageNet Visual Recognition Challenge.
\newblock CS 231N, Stanford University, 2015.

\bibitem{liu2020reactnet}
Z.~Liu, Z.~Shen, M.~Savvides, and K.-T.~Cheng.
\newblock ReActNet: Towards Precise Binary Neural Network with Generalized Activation Functions.
\newblock \emph{ECCV}, 2020.

\bibitem{guo2022bnext}
N.~Guo, J.~Bethge, C.~Meinel, and H.~Yang.
\newblock BNext: Any Precision Binary Neural Network.
\newblock \emph{arXiv:2211.12933}, 2022.

\bibitem{dong2020hawqv2}
Z.~Dong, Z.~Yao, D.~Arfeen, A.~Gholami, M.~W.~Mahoney, and K.~Keutzer.
\newblock HAWQ-V2: Hessian Aware trace-Weighted Quantization of Neural Networks.
\newblock \emph{NeurIPS}, 2020.

\bibitem{qin2020irnet}
H.~Qin, R.~Gong, X.~Liu, M.~Shen, Z.~Wei, F.~Yu, and J.~Song.
\newblock Forward and Backward Information Retention for Accurate Binary Neural Networks.
\newblock \emph{CVPR}, 2020.

\bibitem{zhao2024sqakd}
K.~Zhao and M.~Zhao.
\newblock SQAKD: Self-supervised Quantization-Aware Knowledge Distillation.
\newblock \emph{AISTATS}, 2024.

\bibitem{bengio2013estimating}
Y.~Bengio, N.~Léonard, and A.~Courville.
\newblock Estimating or Propagating Gradients Through Stochastic Neurons for Conditional Computation.
\newblock \emph{arXiv:1308.3432}, 2013.

\bibitem{kim2021relaxloss}
J.~Kim, S.~Bhattacharjee, S.~Park, S.~Jung, and Y.~M.~Kim.
\newblock RelaxLoss: Penalty-Free Quantization through Normalized Loss.
\newblock \emph{arXiv:2105.00944}, 2021.

\bibitem{zhang2018mixup}
H.~Zhang, M.~Cisse, Y.~N.~Dauphin, and D.~Lopez-Paz.
\newblock mixup: Beyond Empirical Risk Minimization.
\newblock \emph{ICLR}, 2018.

\bibitem{gundersen2018reproducibility}
O.~E.~Gundersen and S.~Kjensmo.
\newblock State of the Art: Reproducibility in Artificial Intelligence.
\newblock \emph{AAAI}, 2018.

\bibitem{hutson2018ai}
M.~Hutson.
\newblock Artificial Intelligence Faces Reproducibility Crisis.
\newblock \emph{Science}, 359(6377):725--726, 2018.

\bibitem{dodge2019mlchecklist}
J.~Dodge, S.~Gururangan, D.~Card, R.~Schwartz, and N.~A.~Smith.
\newblock Show Your Work: Improved Reporting of Experimental Results.
\newblock \emph{EMNLP}, 2019.

\bibitem{tflite}
TensorFlow Lite Team.
\newblock TensorFlow Lite: Deploy machine learning models on mobile and edge devices.
\newblock \url{https://www.tensorflow.org/lite}, 2023.

\bibitem{pytorch_mobile}
PyTorch Team.
\newblock PyTorch Mobile: End-to-end workflow from training to deployment.
\newblock \url{https://pytorch.org/mobile/}, 2023.

\bibitem{bitblas}
L.~Wang, L.~Lei, L.~Ye, Y.~Zhao, W.~Chen, D.~Lin, X.~Zheng, and C.~Yu.
\newblock BitBLAS: A High-Performance Library for Quantized Deep Learning.
\newblock \emph{arXiv:2410.16144}, 2024.

\bibitem{pytorch_cifar_kuangliu}
K.~Liu.
\newblock Train CIFAR10 with PyTorch.
\newblock \url{https://github.com/kuangliu/pytorch-cifar}, 2017.

\bibitem{pytorch_cifar100_weiaicunzai}
W.~Zhang.
\newblock PyTorch CIFAR-100 Benchmark.
\newblock \url{https://github.com/weiaicunzai/pytorch-cifar100}, 2019.

\bibitem{tiny_imagenet_benchmark}
Y.~Le and X.~Yang.
\newblock Tiny ImageNet Visual Recognition Challenge.
\newblock CS 231N, Stanford University, 2015.

\bibitem{cover2006information}
T.~M.~Cover and J.~A.~Thomas.
\newblock Elements of Information Theory, 2nd Edition.
\newblock Wiley-Interscience, 2006.

\end{thebibliography}
